### 2017-10-13 Regeneron Paper.tex
Fix thing
Fixes

	I assume the following functions are provided by the runtime environment, so that I may use them without defining them beforehand.\par

	\begin{algorithm}\begin{algorithmic}
			\LineComment{Adds \textit{item} to dynamic array \textit{d}}
			\State $Add\ dyn_{d}(item)$
			\\
			\LineComment{Allocates and returns an array of length \textit{len}}
			\State $Array(len)$
			\\
			\LineComment{Allocates and returns an empty dynamic array}
			\State $Dynamic()$
			\\
			\LineComment{Returns the length of array \textit{a}}
			\State $Len_a$
		\end{algorithmic}\end{algorithm}

	\subsection{Mathematical Notation}

	\begin{description}
		\item[$T_m(n)$] Time it takes to allocate memory for an array of size $n$
	\end{description}

@@

	I begin with the implementation for \textit{Add} since it is the most common list operation\footnote{}. Its algorithm is very similar to that of a dynamic array: it resizes the list if it's full, then stores the item and increments the size. The head's size is also incremented since an item is added to it.

@@

	\begin{algorithm}\begin{algorithmic}[1]
			\LineComment{\textit{G} is the \textit{growth function}.}
			\LineComment{It decides the capacity of the next buffer based on the current buffer's capacity.}
			\Function{\textit{G}}{$cap$}
			\Require
			\Statex $cap \geq 4 \land \log_2{cap} \in \mathbb{N}$
			\State \Return $\begin{cases}
			4 & cap = 4\\
			2 * cap & cap \neq 4
			\end{cases}$
			\EndFunction
		\end{algorithmic}\end{algorithm}

@@

@@

>>>>

	I assume the following functions are provided by the runtime environment, so that I may use them without defining them beforehand.

	% TODO: Why is this appearing in the wrong place?
	\begin{algorithm}\begin{algorithmic}
			\LineComment{Adds \textit{item} to dynamic array \textit{d}}
			\State $Add\ dyn_{d}(item)$
			\\
			\LineComment{Allocates and returns an array of length \textit{len}}
			\State $Array(len)$
			\\
			\LineComment{Allocates and returns an empty dynamic array}
			\State $Dynamic()$
			\\
			\LineComment{Returns the length of array \textit{a}}
			\State $Len_a$
		\end{algorithmic}\end{algorithm}

@@

	I begin with the implementation for \addfn since it is the most common list operation\footnote{}. Its algorithm is very similar to that of a dynamic array: it resizes the list if it's full, then stores the item and increments the size. The head's size is also incremented since an item is added to it.

@@

	\begin{algorithm}\begin{algorithmic}[1]
			\LineComment{\textit{G} is the \textit{growth function}.}
			\LineComment{It decides the capacity of the next buffer based on the current buffer's capacity.}
			\Function{\textit{G}}{$cap$}
			\Require
			\Statex $cap \geq 4 \land \log_2{cap} \in \mathbb{N}$
			\If{$cap = 4$}
				\State \Return $4$
			\EndIf
			\State \Return $2 \cdot cap$
			\EndFunction
		\end{algorithmic}\end{algorithm}

@@

	\begin{align*}
	W(n) &= n + R(n) - 1\right)\\
	R(n) &= \begin{cases}
	0 & n = 0\\
	1 & 1 \leq n \leq 4\\
	\lfloor \log_2{(n - 1)} \rfloor & n > 4
	\end{cases}\\
	W(n) &= O(n)
	\end{align*}

	\begin{align*}
	T_n &= P_W \left(T_W W(n) \right)
	\end{align*}

@@

	\begin{align*}
	S(n) = O(2^{\lceil \log_2 n \rceil})
	% For dynamic arrays, it's this O(2^{\lceil \log_2 n \rceil}).
	\end{align*}
